% The system here for producing my publication list in sections uses biblatex
% and biber to customize the bibliography output. Sections defined by a
% combination of keyword= and custom filtering. See
% http://www.ctan.org/pkg/biblatex

\documentclass{cv}
% Document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{url}
\usepackage{footmisc}

\pagestyle{plain}
\pagenumbering{arabic}

\usepackage[defernumbers=true, bibstyle=authoryear, backend=biber, maxbibnames=10,
    url=false, dashed=false, sorting=ydnt]{biblatex}

\usepackage{hyperref}
\hypersetup{ % turn off the boxes round URLs
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\addbibresource{matthew_brett.bib}
\addbibresource{cv.bib}

\AtEveryBibitem{\clearlist{language}} % clears language

% This stuff below was the result of trial and error to get the bibliography
% output to a) preserve the subsequent paragraph indentation as indicated by
% the adjustwidth environments, and b) To have the correct indentation for
% each entry in the bibliography.  The source from which I was working was
% http://tex.stackexchange.com/questions/46298/printing-bibliography-with-biblatex-in-tufte-handout-fullwidth-environment
\defbibenvironment{bibliography}
  {\list{}{%
          \leftmargin\bibhang
  }}
  {\endlist}
    {\item}

\AtEveryBibitem{\hskip-\bibhang}

% Select methods and statistics entries in bib database
\defbibfilter{methodsOrStatistics}{%
    keyword=methods or keyword=statistics
}

\newcommand{\PlaceDate}[2]{{\bf #1} \hfill {\em #2} \\}
\newcommand{\PlaceDateNote}[3]{{\bf #1} \hfill {\em #2} \\#3}
\newcommand{\UoB}{University of Birmingham}
\newcommand{\UCB}{University of California, Berkeley}
\newcommand{\CBU}{MRC Cognition and Brain Sciences Unit, Cambridge}
\newcommand{\Pkg}[1]{{\tt #1}}

\begin{document}

\nocite{*}

{\huge \bf Matthew Brett}

46 Sir Johns Road \\
Birmingham B29 7ER \\
+44 7722 955505 \\
matthew.brett@gmail.com

\begin{cvSection}{Education}

\PlaceDate{Royal London Hospital}{1987--1990 }
Bachelor of medicine and surgery

\PlaceDateNote{Cambridge University}{1984--1987 }{
Open entrance scholarship \\
BA Experimental psychology}

\end{cvSection}

\begin{cvSection}{Work history}

\PlaceDateNote{Independent teaching, development and research}{September 2021--present}{
    Principal investigator on Chan Zuckerberg Initiative grant for open source software and teaching in brain imaging.

    Contractor for Numfocus non-profit for open-source scientific software.

    Contractor on Covid / sexual offending grant at \UoB.}

\PlaceDateNote{\UoB}{2017--September 2021 }{
    Lecturer in data science}

\PlaceDateNote{\UCB}{2008--2017 }{
    Associate researcher at the Brain Imaging Center}

\PlaceDateNote{\CBU}{2005--2008}{
    Senior investigator scientist in brain imaging methods}

\PlaceDateNote{\UCB}{2003--2005 }{
    Associate specialist in psychology}

\PlaceDateNote{\CBU}{1999--2003 }{
    Research associate in psychology}

\PlaceDateNote{
MRC Cyclotron Unit, Hammersmith Hospital / Physiology Laboratory, Oxford}
{1996--1999}
{Research registrar in neurology}

\PlaceDateNote{Radcliffe Infirmary, Oxford}
{1995--1999}
{Neurology registrar}

\PlaceDateNote{National Hospital for Neurology, London}{1994--1995 }{
Neurology senior house officer}

\PlaceDateNote{St Bartholemew's Hospital, London}{1992--1994 }{
Senior house officer in medicine}

\PlaceDateNote{Addenbrooke's Hospital, Cambridge}{1992 }{
Senior house officer in neurosciences}

\PlaceDateNote{Royal London Hospital}{1991 }{
House officer in medicine}

\PlaceDateNote{Princess Alexandra Hospital, Harlow}{1990 }{
House officer in surgery}

\end{cvSection}

\begin{cvSection}{Research metrics}[
    \footnote{ From
    \url{https://scholar.google.com/citations?user=q12RP7AAAAAJ} as of Jan,
2022}]

{\bf Citations}: 30513 \\
{\bf h-index}: 40 \\
{\bf i10-index}: 52

\end{cvSection}

\begin{cvSection}{Reviewer, editor}

    PLOS One, F1000, NeuroImage; Human Brain Mapping; Journal of Cognitive
    Neuroscience; Neuroscience Letters; Clinical Neurophysiology; Journal of
    Neuroimaging; the Journal of Clinical and Experimental Neuropsychology;
    Frontiers in Neuroinformatics; Computing in Science and Engineering;
    Frontiers in Brain Imaging Methods; Frontiers in Neuroanatomy.  I have just
    accepted an invitation to be an associate editor for Frontiers in Brain
    Imaging Methods.

\end{cvSection}

\begin{cvSection}{Structure of this CV}

        My career has covered an unusual range, and so a standard chronological
        CV would be a patchwork of the different fields in which I have worked.

        For clarity, the rest of this CV is in sections for the somewhat
        separable components of my work:

        \begin{itemize}
            \item Data science
            \item Cognitive and motor neuroscience
            \item Imaging methods and statistics
            \item Scientific computing
            \item Neurology
        \end{itemize}

\end{cvSection}

\begin{cvSection}{Data science}

\begin{cvSubSection}{Teaching}

\PlaceDateNote{\UoB}{2019--September 2021}
    {Two (beginner and intermediate) 10-credit courses in data science for
    ~70 second year neuroscience undergraduates and psychology masters
    students. Course based on the Berkeley data teaching model, but with a
    large proportion of my own material, and many adaptations to the Berkeley
    material.  No requirements for mathematics beyond GCSE or prior experience
    of programming.  Teaches data analysis using Python and the Jupyter
    notebook.  All course materials and exercises available under a free and
    open license online.  Current textbook:
    \url{https://matthew-brett.github.io/cfd2020}.}

\PlaceDateNote{\UoB}{2019--2021}
    {R and data analysis component for ~40 master's students in atmospheric
    data processing and pollution}.

\PlaceDateNote{\UoB}{2019--2020}
    {New course component introducing R and
    data analysis for ~280 first-year geography undergraduates, replacing
    previous teaching in SPSS. Uses combination of lectures, workshops,
    introductory tutorials on DataCamp, and teaching in the R notebook for
    demonstrations, workshops and exercises.}

\PlaceDateNote{\UoB}{2019}
    {Author of free absolute beginner's interactive DataCamp tutorial on R ``R
    from Scratch'': \url{https://campus.datacamp.com/courses/r-from-scratch}.}

\PlaceDateNote{\UoB}{2019--present}
    {Contract for new edition of 1997 book ``Resampling: the new statistics''
    by Julian Simon: \url{https://www.resample.com/intro-text-online}.  The new
    edition will replace code in the custom programming language used by Simon
    with two editions, one with code in Python and another with code in R.  The
    book will be freely available for download, and as a paid print edition}.

\PlaceDateNote{\UoB}{2018--2020}
    {First year two-term 10-credit undergraduate course on data science ``Data
    science for everyone''.  For ~40 undergraduates from any subject in the
    University, with no prior requirements for mathematics or programming.  The
    course was one of a suite of optional first-year modules called "Widening
    Horizons"; the University closed the Widening Horizons programme in 2020.}

\PlaceDateNote{\UoB}{2018--2021} {New course component introducing R and
    data analysis for ~280 second-year Bioscience undergraduates, replacing
    previous teaching in Excel.}

\PlaceDateNote{\UoB}{2018--2021}
    {Organizer and main speaker for monthly peer-learning group on data science
    and scientific computing: ``The Hacker Within''.}

\PlaceDateNote{\UCB}{2016}
{Lead instructor for Berkeley post-graduate course ``PSYCH 214 -- functional
    MRI methods'' \url{https://bic-berkeley.github.io/psych-214-fall-2016}
    using code-first teaching methods and reproducible research practice such
    as version control, testing, code review and data validation.}

\PlaceDateNote{\UCB}{2015}
{Co-taught with Jarrod Millman.  Undergraduate and masters course for the
    statistics department on ``Reproducible and collaborative statistical data
    science''.  We taught Python programming, reproducible research practice
    (as above) and neuroimaging as an example application area.  We wrote up
    this course in Millman et al 2018 (see below).}

\PlaceDateNote{\UCB}{2013--2015} {Organizer, designer and main teacher for
    ``practical neuroimaging'' post-graduate course -- used Python and Jupyter
    notebooks to combine teaching of concepts behind imaging analysis with
    training in scientific computing.}

\PlaceDateNote{\UCB}{2016} {Certified as instructor for Software Carpentry
    workshops \footref{swc}.}

\PlaceDateNote{Havana, Cuba}{2013} {Invited speaker and teacher at the
    Latin-American summer school on Neuroinformatics, speaking on ``The need
    and methods for reproducible science''}

\PlaceDateNote{Lawrence Berkeley National Laboratory}{2012} {Instructor for
    Software Carpentry \footnote{ Software carpentry
    (\url{http://software-carpentry.org}) is an international project to teach
    scientists effective use of computing tools \label{swc}} boot-camp}

Also see code-first teaching for imaging methods in {\bf Imaging methods and
    statistics}.

\end{cvSubSection}

\begin{cvSubSection}{Reproducible science}

\PlaceDateNote{Reproducible science in brain imaging}{2005--present}
{Author of the first (to my knowledge) fully reproducible imaging analysis
    (Aston {\em et al} 2006).  Teaching on reproducible science in brain
    imaging as above.

\end{cvSubSection}

\begin{cvSubSection}{Data science grants}

\PlaceDateNote{Chan Zuckerberg Initiative grant from Essential Open Source
    Software Grant series}{2021--2022} {PI and main author of ``Strengthening
    community and code foundations for brain imaging''. The grant supports
    further work on my Nibabel library for brain imaging (see below), but also
    development of online, free code-first imaging courses on the model of my
    previous Berkeley courses on reproducible science and brain imaging (see
    above).}

\end{cvSubSection}

\begin{cvSubSection}{Data science and reproducibility articles}

\printbibliography[heading=none,
    keyword=datascience,
    keyword=article,
notkeyword=omit]

\end{cvSubSection}

\end{cvSection}

\begin{cvSection}{Cognitive and motor neuroscience}

\begin{cvSubSection}{Neuroscience awards}

{\bf British brain and spine foundation training fellowship} \hfill {\em
1996--1999}

\end{cvSubSection}

\begin{cvSubSection}{Neuroscience teaching}

\PlaceDateNote{Cambridge University}{2007--2008}{
Supervision in undergraduate neuroscience for Jesus College}

\end{cvSubSection}

\begin{cvSubSection}{Neuroscience research supervision}

\PlaceDateNote{\CBU}{2007--2008}
{Member of the Graduate Committee}

\PlaceDateNote{Cambridge University BA final year projects}{2007--2008}
{Final year undergraduate projects in experimental psychology by Sam Burnand
and Rich Armstrong.  Projects on functional MRI of response selection.  Both
projects graded as first class}

\PlaceDateNote{Cambridge University PhD}{2001--2004}
{Jessica Grahn: {\em The functional anatomy of musical beat perception}.
Jessica is an associate professor in the Brain and Mind Institute, Western
University, Ontario}

\PlaceDateNote{Cambridge University PhD}{2000--2004}
{Katja Osswald: {\em The role of SMA and basal ganglia in motor learning,
mechanisms of apraxia and methods of functional MRI analysis}. Katja is an
associate lecturer at the department of psychology in York and an NHS clinical
psychologist}

\end{cvSubSection}

\begin{cvSubSection}{Neuroscience articles}

\printbibliography[heading=none,
    keyword=movethink,
    keyword=article,
notkeyword=omit]

\end{cvSubSection}

\begin{cvSubSection}{Neuroscience abstracts}

\printbibliography[heading=none,
    keyword=movethink,
    keyword=abstract,
notkeyword=omit]

\end{cvSubSection}

\end{cvSection}

\begin{cvSection}{Imaging methods and statistics}

\begin{cvSubSection}{Methods leadership}

Also see {\bf Data Science} section for advocacy of reproducible science in
    brain imaging.

\PlaceDateNote{Development strategy}{2005--present}
{Standard imaging software uses languages unsuitable for large projects
    (MATLAB, C) and / or scientific developers (C, C++).  This makes large
    projects stagnate, discourages scientist developers, and encourages
    uncritical application of software recipes.  Identified Python as the
future standard for scientific development, and started long-term project to
develop open international projects for imaging analysis in Python (see
Computing leadership, Selected software).  }

\PlaceDateNote{Methods reporting}{2008}
{One of six authors on the standard guidelines for reporting an FMRI study
(Poldrack {\em et al} 2008).}

\PlaceDateNote{Hypothesis testing}{2001--present}
{Much initial research followed the emphasis of imaging software on
    exploratory analysis rather than testing anatomical hypotheses.
    Implemented small volume correction methods for SPM software, and wrote
    MarsBaR -- a widely used region-of-interest analysis toolbox for SPM (see
Selected software).  With Rebecca Saxe, Nancy Kanwisher, advocated
region-of-interest methods (Saxe {\em et al} 2006).}

\PlaceDateNote{Understanding imaging statistics}{1996--present} {It is common
    for researchers to find it difficult to relate the statistics they have
    been taught to the statistics implemented in neuroimaging software.  Wrote
    a series of popular online tutorials mixing code and mathematics to
    describe imaging statistics in standard terms, including smoothing, the
    general linear model and random field theory. For some recent examples
    please see \url{https://matthew-brett.github.io/teaching}.}

\end{cvSubSection}

\begin{cvSubSection}{Methods teaching}

    For neuroimaging / data science teaching from 2015, see {\bf Data science}
    section.

\PlaceDateNote{\UCB}{2015--2017}
{Organizer: imaging analysis discussion group}

\PlaceDateNote{\UCB}{2008--2015}
{Lecturer on functional MRI spatial processing and statistics for
post-graduate ``Functional MRI methodology seminar''}

\PlaceDateNote{Stanford University}{2013}
{Lecturer at the ``fMRI data analysis workshop''}

\PlaceDateNote{\UCB}{2008--2011}
{Speaker for post-graduate ``Neuroimaging seminar series''}

\PlaceDateNote{San Francisco}{2009}
{Lecturer on FMRIB Software Library course, speaking on ``Experimental
design''}

\PlaceDateNote{\CBU}{1999--2003, 2005--2008}
{Organizer (1999--2003) and regular speaker at ``Imaging interest group''
seminar series}

\PlaceDateNote{\CBU}{2007}
{Lecturer for short course on SPM}

\PlaceDateNote{Human Brain Mapping conference}{2004, 2006, 2007}
{Lecturer for introductory training course on functional MRI}

\PlaceDateNote{Oslo, Norway}{2005}
{Co-organized and co-taught with Ansgar Furst. 4-day course on FMRI analysis
using SPM software}

\PlaceDateNote{Yale}{2005}
{Faculty for course on anatomical and functional MRI analysis using SPM}

\PlaceDateNote{Paris, France}{2000--2003}
{Lecturer on statistics and spatial processing for functional imaging analysis
course}

\PlaceDateNote{Melbourne, Australia}{2001}
{Only teacher of 9 hours of lectures and 5 hours of practical sessions on
functional MRI analysis using SPM software}

\end{cvSubSection}

\begin{cvSubSection}{Methods research supervision}

\PlaceDateNote{Cambridge University post-doctoral research}{2002--2006}
{Ferath Kherif, working on multivariate statistics for clustering and
diagnostics of functional imaging data. Ferath is a principal investigator at
the Laboratory of Research in Neuroimaging, Lausanne, Switzerland}

\PlaceDateNote{Cambridge University post-doctoral research}{2001--2002}
{Alexandre Andrade, on brain surface-based functional MRI statistics, coherence
analysis.  Alexandre is assistant professor at the Physics Department of the
Faculty of Sciences of the University of Lisbon}

\end{cvSubSection}

\begin{cvSubSection}{Methods articles}

\printbibliography[heading=none,
    keyword=methods,
    keyword=article,
notkeyword=omit]

\end{cvSubSection}

\begin{cvSubSection}{Methods abstracts}

\printbibliography[heading=none,
    keyword=methods,
    keyword=abstract,
notkeyword=omit]

\end{cvSubSection}

\end{cvSection}

\begin{cvSection}{Scientific computing}

\begin{cvSubSection}{Computing leadership}

\PlaceDateNote{Neuroimaging in Python project}{2004--present}
{Co-founder (with Jarrod Millman) of the neuroimaging in Python project (NIPY)
    \url{http://nipy.org}.  Co-author (with Jarrod Millman) of R01 grant to
    fund NIPY development (see below).  PI for grant supporting Nibabel and
    teaching (see {\bf Data Science} above). Set NIPY community development
    standards including BSD code license, version control, continuous
    integration testing on all major platforms, automated reporting of code
    test coverage, formal code review.  The NIPY organization
    \url{https://github.com/nipy} is now home to 12 neuroimaging code projects.
    Lead author and maintainer of \Pkg{nibabel} and \Pkg{nipy} software
    projects; third contributor by code commits of \Pkg{dipy} software project
    (see below).  99th centile personal ranking for scientific code impact by
    Depsy.org \footnote{See: \url{http://depsy.org} and {\em Nature} 2016: 529,
115–116\label{depsy}}}

\PlaceDateNote{Scientific Python}{2004--present}
{Code contributor to all the main scientific Python packages, including
    \Pkg{numpy, scipy, matplotlib, Cython, statsmodels}; organization member of
    projects \Pkg{numpy, scipy, matplotlib, scikit-image, Python-pillow,
    MacPython} and the Python packaging authority.  Author on recent Nature
    papers for both Numpy and Scipy}

\end{cvSubSection}

\begin{cvSubSection}{Computing grants}

\PlaceDateNote{NIH RO1 grant}{2007--2010}
{Co-author (with Jarrod Millman) of NIH grant 5R01MH081909-02 ``Continued
    development and maintenance of the Neuroimaging In Python project''}

    Also see \{bf Data Science} section for Chan Zuckerberg Initiative grant to
    support Nibabel and teaching.

\end{cvSubSection}

\begin{cvSubSection}{Selected scientific software}

See \url{https://www.openhub.net/accounts/matthew-brett}

\PlaceDateNote{Dipy}{2009--present}
{Python package for analysis of diffusion MRI data.  Third-ranked developer by
    code commits.  In total: project has 69 contributors; 43,806 lines of code;
    estimated 11 years of developer effort
\footnote{\url{https://www.openhub.net/p/dipy}}. 99th centile for research
impact among all scientific R and Python projects \footref{depsy}.}

\PlaceDateNote{Nibabel}{2007--present}
{Reads and writes standard neuroimaging file
    formats.  Lead developer and maintainer.  In total: 46 contributors;
    28,473 lines of code; estimated 7 years of developer effort
    \footnote{\url{https://www.openhub.net/p/nibabel}}.  100th centile for
    research impact among all R, Python projects \footref{depsy}.}

\PlaceDateNote{Nipy}{2006--present}
{Spatial processing and statistical analysis
of functional MRI data.  Lead developer and maintainer.  In total: 59
contributors; 69,522 lines of code; estimated 18 years of developer effort
\footnote{\url{https://www.openhub.net/p/nipy}}.  97th centile for research
impact among all R, Python projects \footref{depsy}.}

\PlaceDateNote{Phiwave}{2004--2005}
{Wavelet analysis for spatial inference on
functional imaging data.  Lead developer and maintainer.  2 contributors;
5,367 lines of code; estimated estimated 2 years of effort
\footnote{\url{https://www.openhub.net/p/phiwave}}.}

\PlaceDateNote{MarsBaR}{2003--present}
{Region of interest analysis for functional
    imaging data.  Lead developer and maintainer.  In total: 3 contributors;
22,166 lines of code; estimated 6 years of developer effort
\footnote{\url{https://www.openhub.net/p/marsbar}}.  MarsBaR abstract has been
cited 2289 times as of January 2017.}

\end{cvSubSection}

\begin{cvSubSection}{Computing teaching}

    See: data science teaching; and teaching on imaging methods and statistics.

    For selected recent computing tutorials, see
    \url{https://matthew-brett.github.io/teaching}.

\end{cvSubSection}

\begin{cvSubSection}{Computing articles}

\printbibliography[heading=none,
    keyword=computing,
    keyword=article,
notkeyword=omit]

\end{cvSubSection}

\begin{cvSubSection}{Computing abstracts}

\printbibliography[heading=none,
    keyword=computing,
    keyword=abstract,
notkeyword=omit]

\end{cvSubSection}

\end{cvSection}

\begin{cvSection}{Neurology}

\begin{cvSubSection}{Neurology qualifications}

National training number in neurology (UK) \hfill {\em 1996} \\
Member of the Royal College of Physicians (UK) \hfill {\em 1994}

\end{cvSubSection}

\begin{cvSubSection}{Neurology teaching}

\PlaceDateNote{Oxford University}{1994--1995}{
Supervision of medical students in neuroanatomy}

\end{cvSubSection}

\begin{cvSubSection}{Neurology articles}

\printbibliography[heading=none,
    keyword=neurology,
notkeyword=omit]

\end{cvSubSection}

\end{cvSection}

\end{document}
